### 2014-11-13 tex/abstract.tex

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  These techniques however, exacerbate the path explosion
problem.  In this work, we present a summary heap approach which takes
inspiration from the static analysis domain and defines a bipartiate
graph to encode multiple heaps in single representation, which, unlike
state-of-the-art static analysis approaches, (i) supports aliasing,
(ii) does not require rewrite of constraints on heap updates, and
(iii) can initialize the heap-on-the-fly. We also define a summary
heap algorithm to perform heap updates during symbolic execution on
this representation in order to mitigate the path explosion problem in
GSE techniques. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder framework shows the summary heap
enables the initialization of larger, more complex heaps than
previously possible.

>>>>

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  These techniques however, exacerbate the path explosion
problem.  In this work, we present a summary heap approach which takes
inspiration from the static analysis domain and defines a bipartite
graph to encode multiple heaps in single representation, which, unlike
state-of-the-art static analysis approaches, (i) supports aliasing,
(ii) does not require rewrite of constraints on heap updates, and
(iii) can initialize the heap-on-the-fly. We also define a summary
heap algorithm to perform heap updates during symbolic execution on
this representation in order to mitigate the path explosion problem in
GSE techniques. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder framework shows the summary heap
enables the initialization of larger, more complex heaps than
previously possible.
